\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{hyperref}

\setlength{\textwidth}{6.5in}
\setlength{\textheight}{9in}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\headsep}{0in}
\setlength{\headheight}{0in}
\setlength{\topmargin}{0in}

\title{LHS CS Club: Resources}
%\author{}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle

\section{Links}
\begin{itemize}
\item \url{http://usaco.org/}: USACO home page.
\begin{itemize}
\item Contests page: all USACO contest problems from the past few years.
\item Resources page: more resources.
\end{itemize}
\item \url{http://train.usaco.org/usacogate}: USACO training pages.
\begin{itemize}
\item Contains readings and practice problems of increasing difficulty.
\item A great way to practice for USACO, despite being slightly outdated for very advanced topics.
\end{itemize}
\item \url{http://www.hsin.hr/coci/}: Past COCI contests.
\item \url{http://codeforces.com/contests}: Codeforces contests.
\item \url{https://activities.tjhsst.edu/sct/index.php}: Thomas Jefferson High School's computer team website.
\begin{itemize}
\item Lectures page: links to great readings on various CS topics.
\item Links page: more resources.
\end{itemize}
\item \url{https://www.dropbox.com/s/z2lur71042pjaet/guide.pdf?dl=0}: A very good online book on algorithms useful for coding competitions. (Linked from the TJ website above).
\item \url{https://projecteuler.net/}: Project Euler.
\end{itemize}

\section{Books}
\begin{itemize}
\item {\it Introduction to Algorithms} by Thomas H. Cormen, Charles E. Leiserson, Ronald L. Rivest, Clifford Stein
\item {\it Algorithms} by Robert Sedgewick, Kevin Wayne
\item {\it Algorithms in C++} by Robert Sedgewick
\end{itemize}

\end{document}  